Video Doesn't Lie

### 2016-05-02 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
add be bold

## Acknowledgments
- [NSF BCS-1238599](http://www.nsf.gov/awardsearch/showAward?AWD_ID=1238599&HistoricalAwards=false)
- [NICHD U01-HD-076595](https://projectreporter.nih.gov/project_info_description.cfm?aid=8531595&icde=15908155&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC)
- [Society for Research in Child Development (SRCD)](http://srcd.org)
- NYU Libraries, NYU IT, IRB, and OSP

@@

----
<iframe src="http://doi.org/10.17910/B7H019" width=640px height=400px>
</iframe>

@@

>>>>

## Acknowledgments

- [NSF BCS-1238599](http://www.nsf.gov/awardsearch/showAward?AWD_ID=1238599&HistoricalAwards=false)
- [NICHD U01-HD-076595](https://projectreporter.nih.gov/project_info_description.cfm?aid=8531595&icde=15908155&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC)
- [Society for Research in Child Development (SRCD)](http://srcd.org)
- NYU Libraries, NYU IT, IRB, and OSP

@@

<iframe src="http://doi.org/10.17910/B7H019" width=640px height=400px>
</iframe>

@@

## Join us!

<iframe src="https://databrary.org/about/jobs.html" width=640px height=400px>
</iframe>
